Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-01-27 manuscript.tex
histogram figure
completeness study...

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.20\textwidth}
% 						 p{0.40\textwidth}
% 						 p{0.40\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\
% 		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_depth}  &
% 		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_weekday} &
% 		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_hour}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Catalogue overview. The histogram (a) shows the depth distribution. The histograms (b) and (c) represent the distributions of weekday and hour which earthquakes occur respectively. Dashed lines represent the mean value.}
% 	\label{fig_overview}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\begin{tabular}{ c c }
% 		\footnotesize(a)
% 		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_rate}
% 		\\
% 		\footnotesize(b)
% 		& \includegraphics[width=0.40\textwidth]{z_img_time_mag_count_br_1960}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Earthquakes by year (a) and discriminated by magnitude (b).}
% 	\label{fig_records}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\begin{tabular}{ c c }
% 		\footnotesize(a)
% 		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_decluster}
% 		\\
% 		\footnotesize(b)
%         & \includegraphics[width=0.40\textwidth]{z_img_hmtk_bsb2014_11_clusters}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Decluster evaluation (a) and the clusters map (b).}
% 	\label{fig_decluster}
% 	\end{center}
% \end{figure}

% \begin{figure}
%     \includegraphics[width=.45\linewidth]{z_img_hmtk_bsb2014_11_completeness}
%     \caption{Completeness}
%     \label{fig_completeness}
% \end{figure}

% \begin{figure}
%     \includegraphics[width=.45\linewidth]{z_img_hmtk_bsb2014_11_recurrence}
%     \caption{Annual earthquake recurrence.}
%     \label{fig_occurrence}
% \end{figure}

@@

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_woo_bandwidth}
% 	\caption{Magnitude dependence bandwidth.}
% 	\label{fig_woo_bandwidth}
% \end{figure}

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_hidi}
% 	\caption{Local bandwidth example.}
% 	\label{fig_helmstetter_hidi}
% \end{figure}

% % % TODO add HI_DI histograms

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_stationary_a}
% 	\caption{Stationary seismic rate}
% 	\label{fig_helmstetter_stationary_rate}
% \end{figure}

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_catalogues}
% 	\caption{Learning and target catalogs.}
% 	\label{fig_helmstetter_catalogues}
% \end{figure}

@@

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.33\textwidth}
% 						 p{0.34\textwidth}
% 						 p{0.33\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\
% 		\includegraphics[height=5cm]{z_img_a_frankel_br}  &
% 		\includegraphics[height=5cm]{z_img_a_woo} &
% 		\includegraphics[height=5cm]{z_img_a_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Smoothed rates comparison: (a) shows \citet{frankel_1995} method smoothed rate results, (b) and (c) represent rates smoothed by \citet{woo_1996} and \citet{helmstetter_2012} methods respectively.}
% 	\label{fig_rates}
% 	\end{center}
% \end{figure}

@@

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.33\textwidth}
% 						 p{0.34\textwidth}
% 						 p{0.33\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\
% 		\includegraphics[height=5cm]{z_img_pga_frankel}  &
% 		\includegraphics[height=5cm]{z_img_pga_woo} &
% 		\includegraphics[height=5cm]{z_img_pga_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{PGA (poe 10\%/50y) comparison for (a) \citet{frankel_1995}, (b) \citet{woo_1996} and (c) \citet{helmstetter_2012} methods.}
% 	\label{fig_pga}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\footnotesize(a)
% 		&
% 		\footnotesize(b)
% 		\\
% 		\includegraphics[width=0.45\textwidth]{z_img_pga_gshap} &
% 		\includegraphics[width=0.45\textwidth]{z_img_pga_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Previous available Brazilian PSHA from (a) GSHAP project and the PSHA proposed by this work (b). }
% 	\label{placeholder}
% 	\end{center}
% \end{figure}

>>>>

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.20\textwidth}
						 p{0.40\textwidth}
						 p{0.40\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_depth}  &
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_weekday} &
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_hour}
		\end{tabular}
	\end{table}
	\caption{Catalogue overview. The histogram (a) shows the depth distribution. The histograms (b) and (c) represent the distributions of weekday and hour which earthquakes occur respectively. Dashed lines represent the mean value.}
	\label{fig_overview}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\begin{tabular}{ c c }
		\footnotesize(a)
		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_rate}
		\\
		\footnotesize(b)
		& \includegraphics[width=0.40\textwidth]{z_img_time_mag_count_br_1960}
		\end{tabular}
	\end{table}
	\caption{Earthquakes by year (a) and discriminated by magnitude (b).}
	\label{fig_records}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\begin{tabular}{ c c }
		\footnotesize(a)
		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_decluster}
		\\
		\footnotesize(b)
        & \includegraphics[width=0.40\textwidth]{z_img_hmtk_bsb2014_11_clusters}
		\end{tabular}
	\end{table}
	\caption{Decluster evaluation (a) and the clusters map (b).}
	\label{fig_decluster}
	\end{center}
\end{figure}

\begin{figure}
    \includegraphics[width=.45\linewidth]{z_img_hmtk_bsb2014_11_completeness}
    \caption{Completeness}
    \label{fig_completeness}
\end{figure}

\begin{figure}
    \includegraphics[width=.45\linewidth]{z_img_hmtk_bsb2014_11_recurrence}
    \caption{Annual earthquake recurrence.}
    \label{fig_occurrence}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_woo_bandwidth}
	\caption{Magnitude dependence bandwidth.}
	\label{fig_woo_bandwidth}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_hidi}
	\caption{Local bandwidth example.}
	\label{fig_helmstetter_hidi}
\end{figure}

\begin{figure}
    \begin{center}
    \begin{table}[H]
        %\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
        \begin{tabular}{ c c }
        \footnotesize(a)
        & \includegraphics[width=0.45\textwidth]{z_img_hi_histogram}
        \\
        \footnotesize(b)
        & \includegraphics[width=0.45\textwidth]{z_img_di_histogram}
        \end{tabular}
    \end{table}
    \caption{(a) $h_i$ and (b) $d_i$ distributions for BSB2014.}
    \label{fig_hidi_distributions}
    \end{center}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_stationary_a}
	\caption{Stationary seismic rate}
	\label{fig_helmstetter_stationary_rate}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_catalogues}
	\caption{Learning and target catalogs.}
	\label{fig_helmstetter_catalogues}
\end{figure}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth}
						 p{0.34\textwidth}
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\
		\includegraphics[height=5cm]{z_img_a_frankel_br}  &
		\includegraphics[height=5cm]{z_img_a_woo} &
		\includegraphics[height=5cm]{z_img_a_helmstetter}
		\end{tabular}
	\end{table}
	\caption{Smoothed rates comparison: (a) shows \citet{frankel_1995} method smoothed rate results, (b) and (c) represent rates smoothed by \citet{woo_1996} and \citet{helmstetter_2012} methods respectively.}
	\label{fig_rates}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth}
						 p{0.34\textwidth}
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\
		\includegraphics[height=5cm]{z_img_pga_frankel}  &
		\includegraphics[height=5cm]{z_img_pga_woo} &
		\includegraphics[height=5cm]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{PGA (poe 10\%/50y) comparison for (a) \citet{frankel_1995}, (b) \citet{woo_1996} and (c) \citet{helmstetter_2012} methods.}
	\label{fig_pga}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\footnotesize(a)
		&
		\footnotesize(b)
		\\
		\includegraphics[width=0.45\textwidth]{z_img_pga_gshap} &
		\includegraphics[width=0.45\textwidth]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{Previous available Brazilian PSHA from (a) GSHAP project and the PSHA proposed by this work (b). }
	\label{placeholder}
	\end{center}
\end{figure}
